---
title: "saosTools"
author: "Bartosz Chrol"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


## Using coordinates of courts
```{r, eval=FALSE}
library("saosTools")
library("sp")
library("plotGoogleMaps")

coordinates(cc_coords) <- ~lon+lat
proj4string(cc_coords) <- CRS("+proj=longlat +datum=WGS84")
invisible(plotGoogleMaps(cc_coords, zcol = "type", mapTypeId = "ROADMAP", legend = TRUE))
```


## Updating framework

Sometimes you may want to keep some judgments--related data on disc instead of downloading it every time you need them. If you also want these datasets to be up-to-date, you need some kind of updating scheme. `update_all` function may come in handy, below there is an example of its usage and whole updating framework.

Let's say you keep only dates of judgments in a data frame in `dates.RDS` file. You also need to keep information about time of the last update, let's say it's `snapshot_times.txt` file. Your updating script could look like:

```{r, eval=FALSE}
# source your specific updating function
source("update_db.R")

# read last time
times <- readLines("snapshot_time.txt")
times <- as.POSIXct(tail(times, 1))

# run proper updating function
update_all(times, update_db)

# write down time, with 1hour correction for possible synchro problems
write(as.character(Sys.time() - 3600), 
      file = "snapshot_time.txt", append = TRUE)
```

You may run this script with `Rscript` or any other tool.
`update_db` is a user specific function, which in this case could look like:

```{r, eval=FALSE}
update_db <- function(judgments) {
  library("saos")
  
  dates <- readRDS("dates.RDS")
  
  new_dates <- extract(judgments, "judgmentDate")
  
  # we need to remove duplicated judgments
  new_dates <- new_dates[! new_dates$id %in% dates$id]
  
  dates <- rbind(dates, new_dates)
  saveRDS(dates, "dates.RDS")
  return()
}
```

